Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-29 extended_catalog/paper/extended_catalog.tex
improvements

%\newcommand{\hl}[1]{{\color{red}#1}}
\newcommand{\hl}[1]{#1}

@@

\begin{abstract}
\hl{
Spatial extension is an important characteristic for correctly
associating LAT sources with their counterparts at other wavelengths
and for obtaining an unbiased model of their spectra.  We present a new
method for quantifying the spatial extension of sources with the Large
Area Telescope (LAT), the primary science instrument on the {\em \fermi
Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
simulations to validate this tool and calculate the LAT's threshold for
detecting the spatial extension of sources.  We then test all sources
in the second \fermi-LAT catalog (2FGL) for extension. We report the
detection of nine spatially extended sources in addition to the twelve
spatially extended sources reported in 2FGL.
}
\end{abstract}

@@

\hl{

@@

\pointlike is important for LAT analyses that require many iterations
such as source localization and extension fitting.  On the other hand,
because \gtlike makes fewer approximations in calculating the likelihood
we expect the spectral parameters found with \gtlike to be slightly more
precise.  Furthermore, because \gtlike is the standard likelihood analysis
package, it has been more extensively validated for spectral analysis.
For those reasons, in the following analysis we used \pointlike to
determine the position and extension of a source and subsequently derived
the spectrum using \gtlike. Both \gtlike and \pointlike can be used to
estimate the statistical significance of the extension of a source and we
required that both methods agree for a source to be considered extended.
We found good agreement between the two methods.  Unless explicitly
mentioned, all \ts, \tsext, and spectral parameters were calculated using
\gtlike with the best-fit positions and extension found by \pointlike.

@@

We simulated point-like sources with various spectral forms using
the LAT on-orbit simulation tool
\gtobssim\footnote{\gtobssim is distributed publicly by the FSSC.} and fit the sources
with \pointlike using both point-like
and extended source hypotheses.  These point-like sources were simulated with a power-law
spectral model with integrated fluxes above 100 \mev ranging from $3\times10^{-9}$ 
to $1\times10^{-6}$ \phflux in six discrete steps and spectral
indices ranging from 1.5 to 3 in four discrete steps.  These values
were picked to represent typical source parameters of LAT-detected
sources. The point-like sources were simulated on top of an isotropic
background with an integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux
taken to be the same as the isotropic spectrum measured by EGRET
\citep{sreekumar_isotropic}.  The Monte Carlo simulation was performed
over a one-year observation period using a representative rocking profile and a
representative livetime fraction of 0.8.  The reconstruction was performed
using photons with energies between 1 \gev to 100 \gev 
and the Pass~7\_V6 (P7\_V6) Source Instrument
Response Function (IRFs, \cite{lat_on_orbit_psf}).  For each 
significantly detected point-like source ($\ts\ge25$), we used \pointlike
to fit the source as an extended source and calculate \tsext.

@@

Figure~\ref{index_sensitivity} shows the threshold for sources of four
spectral indices from 1.5 to 3 and extensions varying from $\sigma=0\fdg1$
to $2\fdg0$.  The LAT's flux threshold for a significant detection
of source extension drops quickly with
increasing source size and reaches a minimum around 0\fdg5. 
Figure~\ref{index_sensitivity} shows
the threshold using photons with energies between 100 \mev and 100 \gev
and also using only 1 \gev to 100 \gev photons.
Except for very large ($>1\degree$) sources, our detection threshold is
not substantially improved by including photons with energies between 100 \mev and
1 \gev.  This is also demonstrated in Figure~\ref{four_plots_ic443}
which shows \tsext for the SNR IC443 computed independently in twelve
energy bins between 100 \mev and 100 \gev. For IC443, which has a
spectral index $\sim2.4$, almost the entire increase in likelihood
modeling the source as being extended comes
from energies above 1 \gev.  On the other hand, other systematic errors
become increasingly important at low energy. For our extension search,
we therefore used only photons with energies above 1 \gev.

\hl{
Figure~\ref{all_sensitivity} shows the flux threshold as a function of
source extension for different background levels ($1\times$, $10\times$,
and $100\times$ the nominal background), different spectral indices,
and two different energy ranges (1 \gev to 100 \gev and 10 \gev to
100 \gev).  The detection threshold is higher for sources in regions of
higher background.  When studying sources only at energies above 1 \gev,
the LAT's detection threshold (defined as the 1 \gev to 100 \gev flux at
which $\langle\tsext\rangle=16$) depends less strongly on the source's
spectral index. The index dependence of the detection threshold is
even weaker when considering only photons with energies above 10 \gev.
Overlaid on Figure~\ref{all_sensitivity} are the LAT detected extended
sources that will be discussed in Sections~\ref{validate_known} and
\ref{new_ext_srcs_section}.  The extension thresholds are tabulated in
Table~\ref{all_sensitivity_table}.

Finally, Figure~\ref{time_sensitivity} shows the LAT's projected
detection threshold to extension with a 10 year
exposure against 10 times
the isotropic background. This background is representative of the
background near the Galactic plane.  For small extended sources, our
detection threshold improves by a factor larger than the square root
of the exposure because at high energies, where we are most sensitive
to extension, the background levels are in the Poisson instead of the
Gaussian regime.  For large extended sources, the relevant background
is over a larger spatial range and so the improvement is closer to the
expected factor corresponding to the square root of the exposure.
}

@@

We also performed a search for extended sources using only 10 \gev to 100 \gev photons. 
Although this approach tests the same
sources, it is complimentary because the Galactic diffuse
emission is even less dominant above 10 \gev. Furthermore, source
confusion becomes less of a problem since most LAT sources are not
significantly detected at energies exclusively above 10 \gev. So we
expect to be able to resolve harder sources in more complicated regions
by restricting our analysis to higher energies. The $>10$ \gev
analysis is
especially
beneficial for regions near pulsars which are not significantly detected 
above 10 \gev. A similar procedure was
used to detect HESS\,J1825$-$137 and MSH\,15$-$52 with the LAT
\citep{msh1552,fermi_hess_j1825}.

@@

% 2FGL J1856.2+0450c = P72Y3047 for
We inspected each extended source candidate to identify cases in
which the fit was influenced by large-scale residuals in
the diffuse emission and hence the extension measurement was unreliable.
An example of such a case is 
the source 2FGL\,J1856.2+0450c 
shown in Figure~\ref{example_bad_fit}. The
diffuse-emission-subtracted smoothed
counts map shows that
there appears to be large-scale
residual in the diffuse emission
in this region along the Galactic plane.
As a result, 2FGL\,J1856.2+0450c is fit
to an extension of $\sim2\degree$ and the result is statistically significant
with \tsext=45.4. However, by looking at the residuals it is clear
that this complicated region is not fit well.
We did not report as extended sources that fail this inspection.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

% 3 PWN
Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137 were
identified in 2FGL \citep{msh1552,velax,fermi_hess_j1825}.  
HESS\,J1825$-$137 was significantly detected using photons
with energies between 10 \gev and 100 \gev.
To improve our analysis of this source, we removed from our background model the
nearby catalog source 2FGL\,J1823.1$-$1338c which appeared to
represent part of the emission from the extended source.
To avoid confusion with the nearby bright pulsar PSR\,J1509$-$5850, MSH\,15$-$52 had
to be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH\,15$-$52 to be consistent with the published
size but with an extension significance of \tsext=6.5.

@@

Nine extended sources not included in 2FGL were found using this search.
Three were found in our search using 1 \gev 100 \gev photons and six were
found in our search using 10 \gev to 100 \gev photons.  The fit properties of
these nine sources is summarized in Table~\ref{new_ext_srcs_table}.
This table includes for each source the best fit position, extension,
spectrum, source significance, and significance of extension.

The results of our investigation of systematic uncertainties of this
measurement are presented in 
Table~\ref{alt_diff_model_results}.  It
shows a comparison between the fit with a single extended source
hypothesis and the fit assuming the emission originates from two
independent sources and  the
results of the extension fit using variations of the PSF and the galactic
diffuse model described in Section~\ref{systematic_errors_on_extension}.
There is good agreement between \tsext and the fit size using
the standard analysis, the alternative diffuse models, and the alternative PSF.
This suggests that the sources are robust against features in the diffuse
model and uncertainties in the angular resolution.

@@

The source 2FGL\,J0823.0$-$4246 was found 
to have an 
extension of $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ 
with an extension
significance of $\tsext=46.3$
using 1 \gev to 100 \gev photons.  This source was fit to a position of
$(l,b)=(260\fdg32,-3\fdg28)$.  
This source is coincident with the one-year
catalog source 1FGL\,J0823.3$-$4248.
\hl{
Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source
and Figure~\ref{snr_seds} shows its spectrum.
}
To get a good fit of this source, we removed from our background
model the nearby catalog
sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254 which are part of the
extended source.  These modifications are
shown in Figure~\ref{1FGL_J0823.3-4248}.

\hl{
This extended source is spatially coincident with the
middle-aged SNR Puppis A.  Puppis A has been studied in detail
in radio (\cite{puppis_a_vla}, and references therein) and  X-ray
(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein) Mosaic
\rosat observations of Puppis A produced the highest resolution X-ray
image of this source and contours corresponding to this image are
overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the inferred
size at \gev energies \citep{rosat_puppis_a}.  Puppis A's distance
was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} which leads
to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.
No molecular clouds have been observed directly adjacent to Puppis A
\citep{co_eastern_puppis_a}.  This is similar to the LAT detected Cyngus
Loop SNR \citep{cygnus_loop_lat}.  The luminosity of Puppis A is also
smaller than that of other SNRs believed to interact with molecular clouds
\citep{w51c,ic443,w44,w28,w49b_lat}.
\citep{cygnus_loop_lat}.
}

@@

The source 2FGL\,J1627.0$-$2425c was found  to
have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
an extension significance of $\tsext=31.1$
using 1 \gev to 100 \gev photons.  The best fit position is
$(l,b)=(353\fdg08, 16\fdg78)$.  This source is coincident with the one
year catalog source 1FGL\,J1628.6$-$2419c.  A counts map showing this source
is seen in Figure \ref{1FGL_J1628.6-2419c}.

\hl{
This source is in a region of remarkably complicated diffuse emission.
Even though it is $16\degree$ from the Galactic plane, this source is on
top of the core of the Ophiuchus molecular cloud which contains massive
star-forming regions that are bright in the infrared.  The region also has
abundant molecular and atomic gas traced by CO and HI but also plenty of
dark gas found only by its association with dust emission
\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
more challenging to measure the column density of dust.  Infared and 
${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c}. There is good
spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}
so this source might 
represent $\gamma$-ray emission from the interactions of cosmic rays with
interstellar gas which has not been accounted for in the LAT diffuse
emission model.
}

@@

The source 2FGL\,J1712.4$-$3941 was found 
photons to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
with an extension significance of $\tsext=39.6$
using 1 \gev to 100 \gev.  This source was
fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  this source
is coincident with the one-year catalog source 1FGL\,J1711.7$-$3944c.
Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.

This source is spatially coincident with the SNR RX\,J1713.7$-$3946
and was recently reported by \citep{rx_j1713_lat}.  
Figure~\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR 
RX\,J1713.7$-$3946 from \citep{rx_j1713_hess}.  To analyze this source,
we used the same background model as the recent LAT publication.
2FGL\,J1715.4$-$4024c is spatially coincident with Source A and was
moved to $(\text{RA},\text{Dec})=(258.84,-40.46)$. Source B was added
at $(\text{RA},\text{Dec})=(258.71,-38.70)$ and Source C was added at
$(\text{RA},\text{Dec})=(257.47,-39.75)$.

@@

The source 2FGL\,J0851.7$-$4635 was found 
to have an
extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ 
with an extension
significance of $\tsext=87.2$
using 10 \gev to 100 \gev photons.  This source was fit to a position of
$(l,b)=(266\fdg29,-1\fdg43)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.

2FGL\,J0851.7$-$4635 is spatially coincident with the SNR Vela Jr.
Overlaid on Figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in
\tev by H.E.S.S \citep{vela_jr_hess}.  The \gev and \tev morphology
match well.  A detailed papers by the LAT Collaboration on Vela Jr. is
in preparation.

To get a good fit of this source, removed from
our background model the nearby catalog
sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, and 2FGL\,J0855.4$-$4625
which are part of the extended source.  In addition, we relocalized
the position of the nearby catalog source 2FGL\,J0854.7$-$4501 to
$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies
in the presence of of the extended source.  In addition, we removed from
our model the
further away catalog sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
because they were not significant above 10 \gev.

@@

The source 2FGL\,J1615.0$-$5051 was found 
photons to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
with an extension significance of \tsext=16.3
using 10 \gev to 100 \gev.  This source
was fit to a position of $(l,b)=(332\fdg38,-0\fdg14)$.
This source is coincident with the one-year catalog source
1FGL\,J1613.6$-$5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
of this source.

This source is less than $1\degree$ away from 2FGL\,J1615.2$-$5138 which is
also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
To get a good fit of both sources, we modeled both sources as
being spatially extended and iteratively fit the position and extension
of each source until obtaining a global best fit.  Before doing this,
We removed from our background model the source 2FGL\,J1614.9$-$5212 because it is
part of 2FGL\,J1615.2$-$5138's. Furthermore, we removed from our model the nearby catalog
sources 2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c because they were not
significant above 10 \gev.  These modifications are further described
in the caption to Figure~\ref{1FGL_J1613.6-5100c}.

2FGL\,J1615.2$-$5138 is spatially coincident with the extended
\tev source HESS\,J1616$-$508 \citep{hess_plane_survey}.  In
Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616$-$508 are overlaid
on 2FGL\,J1615.0$-$5051.  The H.E.S.S. experiment measured an
extension $0.136\pm 0.008$ when fitting this source with an elliptical
2D Gaussian surface brightness.  This size corresponds to a 68\% containment
radius of $\rsixeight=0\fdg21\pm0\fdg01$. This size is comparable to the LAT
size $\rsixeight=0\fdg27\pm0\fdg03$ (see Section~\ref{compare_source_size}).
Figure~\ref{hess_seds} shows that the spectrum of 2FGL\,J1615.0$-$5051
at \gev energies
connects smoothly to the spectrum of HESS\,J1616$-$508 at \tev
energies.

\hl{
HESS\,J1616$-$508 is located in the region of two SNRs, RCW103
(G332.4-04) and Kes~32 (G332.4+0.1) but is not spatially coincident
with either of them \citep{hess_plane_survey}.  HESS\,J1616$-$508 is near
three pulsars PSR\,J1614$-$5048, PSR\,J1616$-$5109, and PSR\,J1617$-$5055
but only PSR\,J1617$-$5055 is energetically favored as being the \tev
emitter \citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.
\cite{hess_plane_survey} speculated that a PWN powered by this young
pulsar could be responsible for the emission of HESS\,J1616$-$508.
Because HESS\,J1616$-$508 is $9\arcmin$ away from PSR\,J1617$-$5055, this would
require an assymetric X-ray PWNe to power the \tev emission. However,
\chandra ACIS observations revealed only an underluminous PWN of
about $\sim1\arcmin$ size around the pulsar which was not oriented
towards the \tev emission, rendering this association as uncertain
\citep{discovery_of_pwn_for_PSR_J1617-5055}.  No other promising
counterparts were observed in observations of X-ray and soft gamma-ray
emission by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
IBIS/ISGRBI, BeppoSAX and \xmmnewton \citep{integral_HESS_J1616-508}.
Finally, \cite{discovery_of_pwn_for_PSR_J1617-5055} found diffuse
emission towards the center of HESS\,J1616$-$508 using archival radio and
infared observations.  Deeper observations will likely be necessary to
understand this region.
}

@@

\hl{
Twelve extended sources were included in 2FGL.  Using two years of
LAT data and a new analysis method, we presented the detection of
nine additional extended sources. We also reanalyze the spatial
shape of the twelve extended sources in 2FGL.  The 21 extended
LAT sources are located close to the Galactic plane 
and their localizations shown in
Figure~\ref{allsky_extended_sources}.  Most of the extended sources are
indeed expected to be of Galactic origin as the distance of extragalactic
sources (with the exception of the local group Galaxies) is typically too
large to resolve them in $\gamma$-rays.

>>>>

@@

\begin{abstract}
Spatial extension is an important characteristic for correctly
associating LAT sources with their counterparts at other wavelengths
and for obtaining an unbiased model of their spectra.  We present a new
method for quantifying the spatial extension of sources with the Large
Area Telescope (LAT), the primary science instrument on the {\em \fermi
Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
simulations to validate this tool and calculate the LAT's threshold for
detecting the spatial extension of sources.  We then test all sources
in the second \fermi-LAT catalog (2FGL) for extension. We report the
detection of nine spatially extended sources in addition to the twelve
spatially extended sources reported in 2FGL.
\end{abstract}

@@

@@

\pointlike is important for LAT analyses that require many iterations
such as source localization and extension fitting.  On the other hand,
because \gtlike makes fewer approximations in calculating the likelihood
we expect the spectral parameters found with \gtlike to be slightly more
precise.  Furthermore, because \gtlike is the standard likelihood analysis
package, it has been more extensively validated for spectral analysis.
For those reasons, in the following analysis we used \pointlike to
determine the position and extension of a source and subsequently derived
the spectrum using \gtlike. Both \gtlike and \pointlike can be used to
estimate the statistical significance of the extension of a source and we
required that both methods agree for a source to be considered extended.
There was good agreement between the two methods.  Unless explicitly
mentioned, all \ts, \tsext, and spectral parameters were calculated using
\gtlike with the best-fit positions and extension found by \pointlike.

@@

We simulated point-like sources with various spectral forms using
the LAT on-orbit simulation tool
\gtobssim\footnote{\gtobssim is distributed publicly by the FSSC.} and fit the sources
with \pointlike using both point-like
and extended source hypotheses.  These point-like sources were simulated with a power-law
spectral model with integrated fluxes above 100 \mev ranging from $3\times10^{-9}$ 
to $1\times10^{-6}$ \phflux in six discrete steps and spectral
indices ranging from 1.5 to 3 in four discrete steps.  These values
were picked to represent typical source parameters of LAT-detected
sources. The point-like sources were simulated on top of an isotropic
background with an integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux
taken to be the same as the isotropic spectrum measured by EGRET
\citep{sreekumar_isotropic}.  The Monte Carlo simulation was performed
over a one-year observation period using a representative rocking profile and a
representative livetime fraction of 0.8.  The reconstruction was performed
using photons with energies between 1 \gev and 100 \gev 
and the Pass~7\_V6 (P7\_V6) Source Instrument
Response Function (IRFs, \cite{lat_on_orbit_psf}).  For each 
significantly detected point-like source ($\ts\ge25$), we used \pointlike
to fit the source as an extended source and calculate \tsext.

@@

Figure~\ref{index_sensitivity} shows the threshold for sources of four
spectral indices from 1.5 to 3 and extensions varying from $\sigma=0\fdg1$
to $2\fdg0$.  The LAT's flux threshold for a significant detection
of source extension drops quickly with
increasing source size and reaches a minimum around 0\fdg5. 
Figure~\ref{index_sensitivity} shows
the threshold using photons with energies between 100 \mev and 100 \gev
and also using only photons with energies between 1 \gev and 100 \gev.
Except for very large ($>1\degree$) sources, our detection threshold is
not substantially improved by including photons with energies between 100 \mev and
1 \gev.  This is also demonstrated in Figure~\ref{four_plots_ic443}
which shows \tsext for the SNR IC443 computed independently in twelve
energy bins between 100 \mev and 100 \gev. For IC443, which has a
spectral index $\sim2.4$, almost the entire increase in likelihood
modeling the source as being extended comes
from energies above 1 \gev.  On the other hand, other systematic errors
become increasingly important at low energy. For our extension search,
we therefore used only photons with energies above 1 \gev.

Figure~\ref{all_sensitivity} shows the flux threshold as a function of
source extension for different background levels ($1\times$, $10\times$,
and $100\times$ the nominal background), different spectral indices,
and two different energy ranges (1 \gev to 100 \gev and 10 \gev to
100 \gev).  The detection threshold is higher for sources in regions of
higher background.  When studying sources only at energies above 1 \gev,
the LAT's detection threshold (defined as the 1 \gev to 100 \gev flux at
which $\langle\tsext\rangle=16$) depends less strongly on the source's
spectral index. The index dependence of the detection threshold is
even weaker when considering only photons with energies above 10 \gev.
Overlaid on Figure~\ref{all_sensitivity} are the LAT detected extended
sources that will be discussed in Sections~\ref{validate_known} and
\ref{new_ext_srcs_section}.  The extension thresholds are tabulated in
Table~\ref{all_sensitivity_table}.

Finally, Figure~\ref{time_sensitivity} shows the LAT's projected
detection threshold to extension with a 10 year
exposure against 10 times
the isotropic background. This background is representative of the
background near the Galactic plane.  For small extended sources, our
detection threshold improves by a factor larger than the square root
of the exposure because at high energies, where we are most sensitive
to extension, the background levels are in the Poisson instead of the
Gaussian regime.  For large extended sources, the relevant background
is over a larger spatial range and so the improvement is closer to the
expected factor corresponding to the square root of the exposure.

@@

We also performed a search for extended sources using only photons with energies
between 10 \gev and 100 \gev. 
Although this approach tests the same
sources, it is complimentary because the Galactic diffuse
emission is even less dominant above 10 \gev. Furthermore, source
confusion becomes less of a problem since most LAT sources are not
significantly detected at energies exclusively above 10 \gev. So we
expect to be able to resolve harder sources in more complicated regions
by restricting our analysis to higher energies. The $>10$ \gev
analysis is
especially
beneficial for regions near pulsars which are not significantly detected 
above 10 \gev. A similar procedure was
used to detect HESS\,J1825$-$137 and MSH\,15$-$52 with the LAT
\citep{msh1552,fermi_hess_j1825}.

@@

% 2FGL J1856.2+0450c = P72Y3047 for
We inspected each extended source candidate to identify cases in
which the fit was influenced by large-scale residuals in
the diffuse emission and hence the extension measurement was unreliable.
An example of such a case is 
2FGL\,J1856.2+0450c 
shown in Figure~\ref{example_bad_fit}. The
diffuse-emission-subtracted smoothed
counts map shows that
there appears to be large-scale
residual in the diffuse emission
in this region along the Galactic plane.
As a result, 2FGL\,J1856.2+0450c is fit
to an extension of $\sim2\degree$ and the result is statistically significant
with \tsext=45.4. However, by looking at the residuals it is clear
that this complicated region is not fit well.
We did not report as extended sources that fail this inspection.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

% 3 PWN
Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137 were
identified in 2FGL \citep{msh1552,velax,fermi_hess_j1825}.  
HESS\,J1825$-$137 was significantly detected using photons
with energies between 10 \gev and 100 \gev.
To improve our analysis of this source, we had to remove
from our background model 
2FGL\,J1823.1$-$1338c which was included in 2FGL to
represent part of the extended emission.
To avoid confusion with the nearby bright pulsar PSR\,J1509$-$5850, MSH\,15$-$52 had
to be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH\,15$-$52 to be consistent with the published
size but with an extension significance of \tsext=6.5.

@@

Nine extended sources not included in 2FGL were found by our 
extended source search.
Three were found when using photons with energies between 1 \gev
and 100 \gev and six were found when using photons with energies
between 10 \gev and 100 \gev.  The spectral and spatial properties of
these nine sources is summarized in Table~\ref{new_ext_srcs_table}.
The results of our investigation of systematic errors 
are presented in Table~\ref{alt_diff_model_results}.  it 
compares the fit extension with an extended source hypothesis
to the fit assuming the emission originates from two independent
point-like sources. For these extended extended sources,
$\tsext>\tsinc$ suggesting that the \gev emission does not originate
from multiple physically distinct sources.
Table~\ref{alt_diff_model_results}
also includes the results of the extension fit
using variations of the PSF and the galactic diffuse model described
in Section~\ref{systematic_errors_on_extension}.  There is good
agreement between \tsext and the fit size using the standard analysis,
the alternative diffuse models, and the alternative PSF.  This suggests
that the sources are robust against features in the diffuse emission
model and uncertainties in the angular resolution of the LAT.

@@

2FGL\,J0823.0$-$4246 was found 
to have an 
extension of $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ 
with an extension
significance of $\tsext=46.3$
using 
 photons with energies between
1 \gev and 100 \gev.  This source was fit to 
$(l,b)=(260\fdg32,-3\fdg28)$ and
is coincident with 1FGL\,J0823.3$-$4248.
Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source
and Figure~\ref{snr_seds} shows its spectrum.
To get a good fit of this source, we had to remove from our background
model the nearby sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254
which were included in 2FGL to represent part of the
extended emission.

This extended source is spatially coincident with the
middle-aged SNR Puppis A.  Puppis A has been studied in detail
in radio (\cite{puppis_a_vla}, and references therein) and  X-ray
(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein) Mosaic
\rosat observations of Puppis A produced the highest resolution X-ray
image of this source and contours corresponding to this image are
overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the inferred
size at \gev energies \citep{rosat_puppis_a}.  Puppis A's distance
was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads
to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs$\,\s^{-1}$.
No molecular clouds have been observed directly adjacent to Puppis A
\citep{co_eastern_puppis_a}, similar to the LAT detected Cyngus
Loop SNR \citep{cygnus_loop_lat}.  The luminosity of Puppis A is also
smaller than that of other SNRs believed to interact with molecular clouds
\citep{w51c,ic443,w44,w28,w49b_lat}.

@@

2FGL\,J1627.0$-$2425c was found  to
have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
an extension significance of $\tsext=31.1$
using photons with energies between 1 \gev and 100 \gev.  The source
was fit to
$(l,b)=(353\fdg08, 16\fdg78)$ and is coincident with 
1FGL\,J1628.6$-$2419c.  
Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.

This source is in a region of remarkably complicated diffuse emission.
Even though it is $16\degree$ from the Galactic plane, this source is on
top of the core of the Ophiuchus molecular cloud which contains massive
star-forming regions that are bright in the infrared.  The region also has
abundant molecular and atomic gas traced by CO and HI but also plenty of
dark gas found only by its association with dust emission
\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
more challenging to measure the column density of dust.  Infared and 
${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c} and show good
spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}.
This source might 
represent $\gamma$-ray emission from the interactions of cosmic rays with
interstellar gas which has not been accounted for in the LAT diffuse
emission model.

@@

2FGL\,J1712.4$-$3941 was found 
to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
with an extension significance of $\tsext=39.6$
using 
photons with energies between
1 \gev and 100 \gev.  This source was
fit to $(l,b)=(347\fdg25,-0\fdg54)$ and is coincident
with 1FGL\,J1711.7$-$3944c.
Figure \ref{2FGL_J1712.4-3941} shows a counts map of this source.
This source is spatially coincident with the SNR RX\,J1713.7$-$3946
and was recently reported by \cite{rx_j1713_lat}.  
Figure~\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR 
RX\,J1713.7$-$3946 from \cite{rx_j1713_hess}.  To analyze this source,
we used the same background source model as the recent LAT publication.

@@

2FGL\,J0851.7$-$4635 was found 
to have an
extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ 
with an extension
significance of $\tsext=87.2$
using photons with energies between 10 \gev and 100 \gev.  
This source was fit to 
$(l,b)=(266\fdg29,-1\fdg43)$ and figure~\ref{Vela_Jr} shows a counts
map of the source.
2FGL\,J0851.7$-$4635 is spatially coincident with the SNR Vela Jr.
Overlaid on Figure~\ref{Vela_Jr} are H.E.S.S. \tev contours of Vela Jr.
\citep{vela_jr_hess}.  The \gev and \tev morphology
match well.  A detailed papers by the LAT Collaboration on Vela Jr. is
in preparation.

To get a good fit of this source, we had to remove from
our background model 
2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, and 2FGL\,J0855.4$-$4625
which were included in 2FGL to account for part of the extended emission.  In addition, we relocalized
2FGL\,J0854.7$-$4501 to
$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies
and we had to remove from our model 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
because they were not significant above 10 \gev.

@@

2FGL\,J1615.0$-$5051 was found 
to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
with an extension significance of \tsext=16.3
using 
photons with energies between
10 \gev and 100 \gev.  This source
was fit to $(l,b)=(332\fdg38,-0\fdg14)$ and
is coincident with 
1FGL\,J1613.6$-$5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
of the source.
It is less than $1\degree$ away from 2FGL\,J1615.2$-$5138 which is
also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
To get a good fit of both sources, we modeled both of them as
being spatially extended and iteratively fit the position and extension
of each source. 
We had to remove from our background model 2FGL\,J1614.9$-$5212 
which was included in 2FGL to account for part of the extended emission.
We also removed from our model 2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c because they were not
significant above 10 \gev.

2FGL\,J1615.2$-$5138 is spatially coincident with the extended
and \tev contours are 
overlaid on Figure~\ref{1FGL_J1613.6-5100c} \citep{hess_plane_survey}.
H.E.S.S. measured an
extension $0\fdg136\pm0\fdg008$ when fitting this source with an elliptical
2D Gaussian surface brightness.  This corresponds to a 68\% containment
radius of $\rsixeight=0\fdg21\pm0\fdg01$, comparable to the LAT
size $\rsixeight=0\fdg27\pm0\fdg03$.
Figure~\ref{hess_seds} shows that the spectrum of 2FGL\,J1615.0$-$5051
at \gev energies
also connects smoothly to the spectrum of HESS\,J1616$-$508 at \tev
energies.

HESS\,J1616$-$508 is located in the region of two SNRs RCW103
(G332.4-04) and Kes~32 (G332.4+0.1) but is not spatially coincident
with either of them \citep{hess_plane_survey}.  HESS\,J1616$-$508 is near
three pulsars PSR\,J1614$-$5048, PSR\,J1616$-$5109, and PSR\,J1617$-$5055.
\citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.
Only PSR\,J1617$-$5055 is energetically capable of powering the
\tev emission
and
\cite{hess_plane_survey} speculated that 
HESS\,J1616$-$508 could be 
a PWN powered by this young
pulsar.
Because HESS\,J1616$-$508 is $9\arcmin$ away from PSR\,J1617$-$5055, this would
require an asymmetric X-ray PWNe to power the \tev emission. 
\chandra ACIS observations revealed an underluminous PWN of
size $\sim1\arcmin$ around the pulsar that was not oriented
towards the \tev emission rendering this association uncertain
\citep{discovery_of_pwn_for_PSR_J1617-5055}.  No other promising
counterparts were observed at X-ray and soft gamma-ray energies
by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
IBIS/ISGRBI, BeppoSAX and \xmmnewton \citep{integral_HESS_J1616-508}.
\cite{discovery_of_pwn_for_PSR_J1617-5055} discovered some additional
diffuse
emission towards the center of HESS\,J1616$-$508 using archival radio and
infared observations. Deeper observations will likely be necessary to
understand this $\gamma$-ray source.

@@

Twelve extended sources were included in 2FGL.  Using two years of
LAT data and a new analysis method, we presented the detection of
nine additional extended sources. We also reanalyze the spatial
shape of the twelve extended sources in 2FGL.  The 21 extended
LAT sources are primarily along the Galactic plane 
and their locations are shown in
Figure~\ref{allsky_extended_sources}.  Most of the LAT detected
extended sources are
expected to be of Galactic origin as the distance of extragalactic
sources (with the exception of the local group Galaxies) is typically too
large to be able to resolve them at $\gamma$-rays energies.
